DeepPicar:​ ​A​ ​Low-cost​ ​Deep​ ​Neural​ ​Network-based​ ​Autonomous​ ​Car

### 2017-10-03 paper/overview.tex
overview revision

\begin{figure}[h]
  \centering
  \includegraphics[width=.4\textwidth]{figs/track_new2}
  \caption{A track for training/testing.\fixme{replace this}}
  \label{fig:track}
\end{figure}

% inferencing on pi3
Once the network is trained on the desktop computer, the trained model
is copied back to the Raspberry Pi computer. The network is then used
by the car's main controller, which feeds an image frame the web
camera as input to the network. The produced steering angle output is
then converted as the PWM value of the steering motor of the
car. Figure~\ref{fig:controlloop} shows simplified psuedo code of the
controller's main loop.

@@

\fixme{Discuss the limitation of the RC car platform: discrete
  control, web camera latency}

%% Although the steering angle output of the network is a continuous
%% real value,

>>>>

\begin{figure}[h]
  \centering
  \includegraphics[width=.4\textwidth]{figs/track_new2}
  \caption{One of the custom tracks used for training/testing.}
  \label{fig:track}
\end{figure}

% inferencing on pi3
Once the network is trained on the desktop computer, the trained model
is copied back to the Raspberry Pi computer. The network is then used
by the car's main controller, which feeds a image frame from the web
camera as input to the network. The produced steering angle output is
then converted as the PWM value of the steering motor of the
car. Figure~\ref{fig:controlloop} shows simplified psuedo code of the
controller's main loop. Among the five steps, step 3---network
inferencing---is most computationally intensive and dominates the
execution time.

@@

Note that although the steering angle output of the network $angle$ is
a continuous real value, the RC car platform we used unfortunately
only supports three discrete angles---left (-30$^{\circ}$), center
(0$^{\circ}$), and right (+30$^{\circ}$)---as control
inputs. Currently, we approximate the network generated real-valued
angle to the closest one of the three angles. Although this may
introduce inaccuracy in control.
In the future, we plan to use different (more expensive) RC car
platforms that can precisely control the car's steering angle. We
would like to stress, however, that the use of different RC car
platforms has no impact in terms of computational 
aspects of the system, and that our main focus of this study is
not in improving network accuracy but in closely replicating the
DAVE-2's network architecture and its real-time characteristics.

Nevertheless, the trained model was still able to achieve reasonable a
degree of accuracy, successfully navigating several different tracks 
we trained. A collection of self-driving videos of the DeepPicar can
be found at: \url{https://github.com/heechul/picar/videos}.
